---
title: "Exercise: Bayesian Inference 1"
author: "Paul Bürkner"
date: "`r Sys.Date()`"
output: html_document
encoding: UTF-8
---

```{r, SETTINGS-knitr, include=FALSE}
# only relevant when knitting the document
options(width = 90)
knitr::opts_chunk$set(
  cache = FALSE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
```


Number of random draws from the prior:
```{r}
n_draws <- 20000
```

Here you sample n_draws draws from the prior  
```{r}
prior <- rbeta(n_draws, 1, 1)
```

It's always good to eyeball the prior to make sure it looks okay.
```{r}
hist(prior)
```

Here to specify the observed data.
```{r}
N <- 10
y_obs <- 4
```

Here you simulate data from the likelihood using the parameters from the prior.
```{r}
y_sim <- rbinom(length(prior), size = N, prob = prior)
```

Here you filter off all draws that do not match the data.
```{r}
posterior <- prior[y_sim == y_obs] 
```

See that we got enough draws left after the filtering. 
There are no rules here, but you probably want to aim for > 400 draws.
```{r}
length(posterior) 
```

Eyeball the posterior:
```{r}
hist(posterior)
plot(density(posterior))
```

Now you can summarize the posterior, where a common summary is to take the mean or the median posterior.
```{r}
mean(posterior)
median(posterior)
```

Exercises:

- Play around with the value of y and N as well as the prior and see how the posterior changes.
